Report

### 2015-08-25 Report Aug 5 2015/Report Aug 2015.tex
Backup

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})-\tilde{R}(\hat{\xi}^{i})))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part vectorized}
\end{IEEEeqnarray}
where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components. 
\section{Work Set Selection and Solver}\label{WSS}
(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.   
Decomposition method is a set of efficient algorithms that can help to conquer this difficulty. Decomposition method works iteratively, the basic idea of decomposition method is to choose a subset of variable pairs $S$ (named work set) to optimize in each iteration step while keep the rest variable pairs $N$ fixed. Sequential Minimal Optimization (SMO) \cite{SMO} is an extreme case of decomposition method, the work set size is 2, an analytic quadratic programming (QP) step instead of numerical QP step can be taken in each iteration.

Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only. By dividing the variables into work set $S$ and fixed set $N$, (\ref{complex duality real part vectorizes}) can be changed to:
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
+Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
\nonumber
\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
-\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r}))),
\label{real part decomposition}
\end{IEEEeqnarray}
Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}^{r}_{SS}& -\mathbf{K}^{r}_{SN}\\
-\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
\end{IEEEeqnarraybox*}\right]$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$
and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed. Therefore the sub-optimization problem is formulated as 
\begin{equation}
maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]-[(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
+Re(\mathbf{y})_{S}^{T}](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
\label{subset optimization}
\end{equation}
In decomposition method, a proper work set selection strategy is required so that acceptable speed and performance can be guaranteed. One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{inproved training algorithms for support vector machines}, Heuristic methods are used in [\cite{SMO}] in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost. Lin propose another work set selection strategy based on an alternative form of KKT condition.

Another class of approaches is to choose the dual variables whose update can provide the maximum improvements to objective function \cite{}, \cite{}, \cite{}(Training without offset). That is 
\begin{equation}
maximize\quad \bigtriangledown \Theta_{S}=\Theta((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta(\alpha, \hat{\alpha}),
\label{maximum gain work set selection}
\end{equation} 
where $\delta_{S}=\alpha_{S}^{new}-\alpha_{S}$
In our regression model, the offset is omitted, therefore different from SMO algorithm, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration. However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}. Here we propose sequential 1-D work set selection, which can approximate the effect of optimal 2-D work set selection. There is only $O(n)$ searching times required for the former one while the later one need $O(n^{2})$ searching times.   
\subsection{Single Direction Solver}
 We will first introduce 1-D work set selection strategy in which the dual variable pair that maximizes the gain of objective function is chosen. Recall the decomposition method in (\ref{maximum gain work set selection}), let $\alpha_{1}$ denotes the dual variable that is chosen to be updated. The sub optimization  problem is formulated as 
 \begin{IEEEeqnarray}[\relax]{l}
 \nonumber
 maximize\quad \Theta_{1}^{r}=-\frac{1}{2}((\alpha_{1}-\hat{\alpha}_{1})^{new})^{2}\mathbf{K}_{11}^{r}-(\alpha_{1}-\hat{\alpha}_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}(\alpha_{j}-\hat{\alpha}_{j})^{new}
+Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})^{new}\\
-\epsilon(\alpha_{1}+\hat{\alpha}_{1})^{new},
 \label{optimization function 1-D}
 \end{IEEEeqnarray}
take the partial derivative of $\Theta_{1}^{r}$ respect to $\alpha_{1}$ and $\hat{\alpha}_{1}$, we have 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \Theta_{1}^{r}}{\partial \alpha_{1}}=-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}-\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}+Re(y_{1})-\epsilon=0\\
\Rightarrow \alpha_{1}^{new}=\alpha_{1}+\frac{\Phi_{1}^{r}-\epsilon}{\mathbf{K}_{11}^{r}},
\label{partial optimization function 1-D alpha}
\end{IEEEeqnarray}

 \begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \Theta_{1}^{r}}{\partial \hat{\alpha}_{1}}=(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}+\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}-Re(y_{1})-\epsilon=0\\
\Rightarrow \hat{\alpha}_{1}^{new}=\hat{\alpha}_{1}-\frac{\Phi_{1}^{r}+\epsilon}{\mathbf{K}_{11}^{r}}\\
\label{partial optimization function 1-D alpha hat}
\end{IEEEeqnarray} 
where we define $\Phi_{i}^{r}=Re(y_{i})-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}$, similarly, as to dual variable  $\beta$ and $\hat{\beta}$, we define $\Phi_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}_{ij}^{r}$. 
Recall complementary KKT condition
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{ll}
(C\tilde{R}(\xi^{r})-\alpha)\xi^{r}=0\\
(C\tilde{R}(\hat{\xi}^{r})-\hat{\alpha})\hat{\xi}^{r}=0\\
\alpha(\epsilon+\xi^{r}-Re(y)+<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
\hat{\alpha}(\epsilon+\hat{\xi}^{r}+Re(y)-<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
\end{array}\right.
\label{complementary KKT condition}
\end{IEEEeqnarray}
it can be easily observed that $\alpha\hat{\alpha}=0$, because $0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(C\tilde{R}(\hat{\xi}^{r}))$,  $\xi^{r}$ and $\hat{\xi}^{r}$ satisfy $\xi^{r}\hat{\xi}^{r}$. The update of $\alpha_{1}$ or $\hat{\alpha}_{1}$ is completed by clipping
\begin{IEEEeqnarray}[\relax]{l}
\alpha^{new\quad clipped}=[\alpha^{new}]_{0}^{C\tilde{R}(\xi^{r})}\\
\hat{\alpha}^{new\quad clipped}=[\hat{\alpha}^{new}]_{0}^{C\tilde{R}(\hat{\xi}^{r})}\\
\label{clipped new dual variable}
\end{IEEEeqnarray}
where $[ ]_{a}^{b}$ denotes to function 
\begin{IEEEeqnarray}[\relax]{l}
[x]_{a}^{b}=\left\{\begin{array}{ll}
a \quad if\quad  x\leq a\\
x \quad if\quad a<x<b\\
b \quad if\quad x\geq b\\
\end{array}\right.
\label{clipping function}
\end{IEEEeqnarray}
Based on (\ref{partial optimization function 1-D alpha}), (\ref{partial optimization function 1-D alpha hat}) and (\ref{clipped new dual variable}), The gain of objective function respect to $i$th dual variable pair is 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\bigtriangledown \Theta_{i}^{r}=\Theta^{r}((\alpha+\delta_{i}\mathbf{e}_{i}), (\hat{\alpha}+\hat{\delta}_{i}\mathbf{e}_{i}))-\Theta^{r}(\alpha, \hat{\alpha})\\
\nonumber
=-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}_{ii}^{r}-(\delta_{i}-\hat{\delta}_{i})\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}+Re(y_{i})(\delta_{i}-\hat{\delta}_{i})-\epsilon(\delta_{i}+\hat{\delta}_{i})\\
=(\delta_{i}-\hat{\delta}_{i})[-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})\mathbf{K}_{ii}^{r}+\Phi_{i}^{r}-\epsilon\frac{\delta_{i}+\hat{\delta}_{i}}{\delta_{i}-\hat{\delta}_{i}}],
\label{gain of objective function}
\end{IEEEeqnarray}
where $\delta_{1}=\alpha^{new\quad clipped}_{1}-\alpha_{1}$, $\hat{\delta}_{1}=\hat{\alpha}^{new\quad clipped}_{1}-\hat{\alpha}_{1}$, in 1-D searching procedure, the dual variable pair which has the maximum gain of objective function is chosen as $1$ in (\ref{optimization function 1-D}), that is 
\begin{equation}
1=arg_{(i=1,\ldots, N_{r})}\max \bigtriangledown \Theta_{i}^{r},
\label{1-D direction}
\end{equation}
\subsection{Double Direction Solver}

\subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}
Recall (\ref{formula9})
\begin{equation}
\phi_{om}=\prod_{i=1}^{N_{t}}\frac{|r_{ii}|^{2}}{|r_{ii}|^{2}+\sum_{j<i}|r_{ji}|^{2}}.
\end{equation}
All the components in $\mathbf{R}$ are independently distributed and $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ \cite{nagar2011expectations}. Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$. Defining $\alpha_{i}=\sum_{j<i}|r_{ji}|^{2}$ and $\beta_{i}=|r_{ii}|^{2}$, $\alpha_{i}$ and $\beta_{i}$ are mutually independent, therefore (\ref{formula9}) can be rewritten as 
\begin{equation}
\phi_{om}=\prod_{i=1}^{N_{t}}\frac{\beta_{i}}{\beta_{i}+\alpha_{i}},
\label{formula21}
\end{equation}
From \cite{gupta2004handbook}, if $X\sim Gamma(k_{1},\theta)$ and $Y\sim Gamma(k_{2},\theta)$, then $\frac{X}{X+Y}\sim B(k_{1},k_{2})$, where $B$ denotes Beta distribution. Therefore $\frac{\beta_{i}}{\beta_{i}+\alpha_{i}}\sim B(k^{i}_{1}, k^{i}_{2})$, where $k^{i}_{1}=N_{r}-i+1$, $k^{i}_{2}=i-1$. we define $\eta_{i}=\frac{\beta_{i}}{\beta_{i}+\alpha_{i}}$, it is obvious that $\eta_{i}$ are independently distributed. Based on (\ref{formula21}), we have 
\begin{equation}
\phi_{om}=\prod_{i=1}^{N_{t}}\eta_{i}.
\label{formula22}
\end{equation}
Therefore the density function of $\phi_{om}$ can be defined as
\begin{equation}
f_{\phi_{om}}(x)=\frac{1}{x}\sum_{\mathbf{j}}(\prod_{i=1}^{N_{t}}c(k_{1}^{i}k,k_{2}^{i},j^{i}))f(-\ln(x)|\mathbf{k_{1}}+\mathbf{j}), 
\label{formula23}
\end{equation}
where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{N_{t}}}$, the range of $j^{i}\in [0, k_{2}^{i}-1]$, $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function. $f(-\ln(x)|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})\ln(x))/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$. $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1},\cdots k_{1}^{N_{t}-1}+j^{N_{t}-1},k_{1}^{N_{t}}+j^{N_{t}}]$. Proof: see Appendix C.

>>>>

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})-\tilde{R}(\hat{\xi}^{i})))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part vectorized}
\end{IEEEeqnarray}
where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components. Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel. In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping condition. Therefore, in large MIMO scenario, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.    
\section{Work Set Selection and Solver}\label{WSS}
(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.

Decomposition method is a set of efficient algorithms that can help to conquer this difficulty. Decomposition method works iteratively, the basic idea of decomposition method is to choose a subset of variable pairs $S$ (named work set) to optimize in each iteration step while keep the rest variable pairs $N$ fixed. Sequential Minimal Optimization (SMO) \cite{SMO} is an extreme case of decomposition method, the work set size is 2, an analytic quadratic programming (QP) step instead of numerical QP step can be taken in each iteration.

Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only. By dividing the variables into work set $S$ and fixed set $N$, we have $(\alpha, \hat{\alpha})=((\alpha_{N}, \hat{\alpha}_{N})\mathbf{e}_{N}+(\alpha_{S}+\hat{\alpha}_{S})\mathbf{e}_{S})$, where $\mathbf{e}_{K}$ denotes the modified vector of $\mathbf{e}$ with the components in set $K$ zeroed, for sake of brevity， we replace $\alpha_{K}\mathbf{e}_{K}$ by $\alpha_{K}$. Thus (\ref{complex duality real part vectorizes}) can be changed to:
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
+Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
\nonumber
\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
-\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r}))),
\label{real part decomposition}
\end{IEEEeqnarray}
Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}^{r}_{SS}& \mathbf{K}^{r}_{SN}\\
\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
\end{IEEEeqnarraybox*}\right]$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$
and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed. Therefore the sub-optimization problem is formulated as 
\begin{equation}
maximize\quad \Theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
\label{subset optimization}
\end{equation}
In decomposition method, a proper work set selection strategy is required so that acceptable speed and performance can be guaranteed. One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{inproved training algorithms for support vector machines}, Heuristic methods are used in [\cite{SMO}] in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost. Lin propose another work set selection strategy based on an alternative form of KKT condition.

Another class of approaches is to choose the dual variables whose update can provide the maximum improvements to objective function \cite{}, \cite{}, \cite{}(Training without offset). That is 
maximize\quad \bigtriangledown \Theta_{S}=\Theta((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta(\alpha, \hat{\alpha}),
\label{maximum gain work set selection}
where $\delta_{S}=\alpha_{S}^{new}-\alpha_{S}$, the gain in (\ref{maximum gain work set selection}) can be written as 
\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}[(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+2(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}]+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}](\delta-\hat{\delta})_{S}\\
-\epsilon(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}
\label{gain work set selection1}
In (\ref{gain work set selection1}), we use 
(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}+(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}=[(\alpha-\hat{\alpha})^{T}_{S}, (\alpha-\hat{\alpha})^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}^{r}_{SS}\\
\mathbf{K}^{r}_{NS}
\end{IEEEeqnarraybox*}\right]=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S},
\label{modification of gain work set selection}
where $\mathbf{K}^{r}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns  that belong to work set $S$. Then we define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}(\alpha-\hat{\alpha})$ and $\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}(\beta-\hat{\beta})$
Thus (\ref{gain work set selection1}) can be rewritten as 
\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}
\label{gain work set selection2}
In our regression model, the offset is omitted, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration. However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}. Here we propose sequential 1-D work set selection, which can approximate the effect of optimal 2-D work set selection. There is only $O(n)$ searching times required for the former one while the later one need $O(n^{2})$ searching times.   
\subsection{Single Direction Solver}
 We will first introduce 1-D work set selection strategy in which the dual variable pair that maximizes the gain of objective function is chosen. Recall the decomposition method in (\ref{maximum gain work set selection}), let $\alpha_{1}$ denotes the dual variable that is chosen to be updated. The sub optimization  problem is formulated as 
 maximize\quad \Theta_{1}^{r}=-\frac{1}{2}((\alpha_{1}-\hat{\alpha}_{1})^{new})^{2}\mathbf{K}_{11}^{r}-(\alpha_{1}-\hat{\alpha}_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}(\alpha_{j}-\hat{\alpha}_{j})
+Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})^{new}\\
-\epsilon(\alpha_{1}+\hat{\alpha}_{1})^{new},
 \label{optimization function 1-D}
take the partial derivative of $\Theta_{1}^{r}$ respect to $\alpha_{1}$ and $\hat{\alpha}_{1}$, we have 
\frac{\partial \Theta_{1}^{r}}{\partial \alpha_{1}}=-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}-\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}+Re(y_{1})-\epsilon=0\\
\Rightarrow \alpha_{1}^{new}=\alpha_{1}+\frac{\Phi_{1}^{r}-\epsilon}{\mathbf{K}_{11}^{r}},
\label{partial optimization function 1-D alpha}

 \begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \Theta_{1}^{r}}{\partial \hat{\alpha}_{1}}=(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}+\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}-Re(y_{1})-\epsilon=0\\
\Rightarrow \hat{\alpha}_{1}^{new}=\hat{\alpha}_{1}-\frac{\Phi_{1}^{r}+\epsilon}{\mathbf{K}_{11}^{r}}\\
\nonumber
\label{partial optimization function 1-D alpha hat}
\end{IEEEeqnarray} 
where we define $\Phi_{i}^{r}=Re(y_{i})-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}$, similarly, as to dual variable  $\beta$ and $\hat{\beta}$, we define $\Phi_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}_{ij}^{r}$. 
Recall complementary KKT condition
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{ll}
(C\tilde{R}(\xi^{r})-\alpha)\xi^{r}=0\\
(C\tilde{R}(\hat{\xi}^{r})-\hat{\alpha})\hat{\xi}^{r}=0\\
\alpha(\epsilon+\xi^{r}-Re(y)+<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
\hat{\alpha}(\epsilon+\hat{\xi}^{r}+Re(y)-<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
\end{array}\right.
\label{complementary KKT condition}
\end{IEEEeqnarray}
it can be easily observed that $\alpha\hat{\alpha}=0$, because $0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(C\tilde{R}(\hat{\xi}^{r}))$,  $\xi^{r}$ and $\hat{\xi}^{r}$ satisfy $\xi^{r}\hat{\xi}^{r}$. The update of $\alpha_{1}$ or $\hat{\alpha}_{1}$ is completed by clipping
\begin{IEEEeqnarray}[\relax]{l}
\alpha^{new\quad clipped}=[\alpha^{new}]_{0}^{C\tilde{R}(\xi^{r})}\\
\hat{\alpha}^{new\quad clipped}=[\hat{\alpha}^{new}]_{0}^{C\tilde{R}(\hat{\xi}^{r})}\\
\nonumber
\label{clipped new dual variable}
\end{IEEEeqnarray}
